---
title: 'W241 Experiments and Causality Final Project'
author: 'Guatam Karnataki, Adara Liao, Yaran Zhang' 
output:
  rmarkdown::github_document
---

**Contents**
Part 1: Process and Generate Clean Survey Data 
Part 2: Generate Modeling Data: add Y and other Outcome Variable for modeling use
Part 3: EDA for Covarites
Part 4: EDA for Outcome Variables
Part 5: Model 1 xxxx
Part 6: Model 2 xxxx
Part 7: xxx

**DataFrame Introcuction**
**d.clean.survey**: clean data direclty from survey, with below fields
**d.clean.model**: clean data from Survey + Outcome Varaibles + Other variables ONLY for modeling purpose


```{r}
# load packages 
library(data.table)
library(foreign)
library(lmtest)
library(stargazer)
library(sandwich)
library(bit64)
library(ggplot2)
library(dplyr)
library(scales)
library(stringr)
library(reshape2)

```


```{r}
##################################### Part 1: Process and Generate Clean Survey Data 
#### result dataframe:  d.clean.survey

# Load survey result from CSV
dsm <- fread("./data/sm_results.csv")
dq <- fread("./data/qualtrics_results.csv")

# Convert column type for merge purpose
dsm <- transform(dsm, year_of_birth =  as.character(year_of_birth))
dsm <- transform(dsm, respondent_id =  as.character(respondent_id))

# Correct column name for SM file
colnames(dsm)[colnames(dsm)=="psyciatrist"] <- "psychiatrist"
colnames(dsm)[colnames(dsm)=="denstist"] <- "dentist"
colnames(dq)[colnames(dq)=="end_Date"] <- "end_date"

# UNION SM result and Q result except for gender-specific columns
d.clean.survey <- rbind(dsm[,c(1:10, 15:18)], dq[, 2:15], fill=TRUE)

# Append gender-specific columns from Q result
d.clean.survey$gender_specific_physician1[d.clean.survey$channel == "qualtrics"] <- "Female"
d.clean.survey$gender_specific_score1[d.clean.survey$channel == "qualtrics"]  <- coalesce(dq$urologist_score1, dq$obgyn_score1)
d.clean.survey$gender_specific_physician2[d.clean.survey$channel == "qualtrics"]  <- "Female"
d.clean.survey$gender_specific_score2[d.clean.survey$channel == "qualtrics"]  <- coalesce(dq$urologist_score2, dq$obgyn_score2)
d.clean.survey$gender_specific_physician3 [d.clean.survey$channel == "qualtrics"] <- "Male"
d.clean.survey$gender_specific_score3[d.clean.survey$channel == "qualtrics"]  <- coalesce(dq$urologist_score3, dq$obgyn_score3)
d.clean.survey$gender_specific_physician4[d.clean.survey$channel == "qualtrics"]  <- "Male"
d.clean.survey$gender_specific_score4[d.clean.survey$channel == "qualtrics"]  <- coalesce(dq$urologist_score4, dq$obgyn_score4)

# Remove irregular words
d.clean.survey$race <- gsub("\xeb_", " ", d.clean.survey$race)
d.clean.survey$income <- gsub("\xeb_", " ", d.clean.survey$income)
d.clean.survey$degree <- gsub("\xeb_", " ", d.clean.survey$degree)
d.clean.survey$income <- gsub("\xeb_", " ", d.clean.survey$income)
d.clean.survey$degree <- gsub("<eb>_", " ", d.clean.survey$degree)

# Set NA
d.clean.survey$pcp[d.clean.survey$pcp == "NULL"] <- NA
d.clean.survey$cardiologist[d.clean.survey$cardiologist == "NULL"] <- NA
d.clean.survey$psychiatrist[d.clean.survey$psychiatrist == "NULL"] <- NA
d.clean.survey$dentist[d.clean.survey$dentist == "NULL"] <- NA

# Make gender value consistent
d.clean.survey$gender[d.clean.survey$gender == "male"] <- "Male"
d.clean.survey$pcp[d.clean.survey$pcp == "male"] <- "Male"
d.clean.survey$cardiologist[d.clean.survey$cardiologist == "male"] <- "Male"
d.clean.survey$psychiatrist[d.clean.survey$psychiatrist == "male"] <- "Male"
d.clean.survey$dentist[d.clean.survey$dentist == "male"] <- "Male"

d.clean.survey$gender[d.clean.survey$gender == "female"] <- "Female"
d.clean.survey$pcp[d.clean.survey$pcp == "female"] <- "Female"
d.clean.survey$cardiologist[d.clean.survey$cardiologist == "female"] <- "Female"
d.clean.survey$psychiatrist[d.clean.survey$psychiatrist == "female"] <- "Female"
d.clean.survey$dentist[d.clean.survey$dentist == "female"] <- "Female"

# Make degree value consistent
d.clean.survey$degree <-  gsub("degree", "Degree", d.clean.survey$degree)
d.clean.survey$degree[d.clean.survey$degree == "High school graduate (high school diploma or equivalent including GED)"] <-  "High School Graduate"
d.clean.survey$degree[d.clean.survey$degree == "Professional Degree (JD, MD)"] <-  "Professional Degree (MD, JD etc.)"


# Make race value consistent
d.clean.survey$race <-  gsub("American Indian or Alaskan Native", "American Indian or Alaska Native", d.clean.survey$race)
d.clean.survey$race <-  gsub("Others not mentioned above", "Others not mentioned", d.clean.survey$race)
d.clean.survey$race <-  gsub("Prefer not to disclose", "Prefer NOT to disclose", d.clean.survey$race)

# Correct year_of_birth data and convert to int
d.clean.survey$year_of_birth <-  gsub("3/22/92", "1992", d.clean.survey$year_of_birth)
d.clean.survey$year_of_birth <-  gsub("5/21/84", "1984", d.clean.survey$year_of_birth)
d.clean.survey$year_of_birth <-  gsub("6/3/80", "1980", d.clean.survey$year_of_birth)
d.clean.survey$year_of_birth <-  gsub("5281993", "1993", d.clean.survey$year_of_birth)
d.clean.survey$year_of_birth <-  gsub("3/29/84", "1992", d.clean.survey$year_of_birth)


# Make income value consistent
d.clean.survey$income[d.clean.survey$income == "$50,000 and $99,999"] <- "$50,000 to $99,999"
d.clean.survey$income[d.clean.survey$income == "$150,000 or $199,999"] <- "$50,000 to $99,999"
d.clean.survey$income[d.clean.survey$income == "More than $199,999"] <- "$200,000 or more"


# Improve format
d.clean.survey$channel <-  gsub("surveymonkey", "SurveyMonkey", d.clean.survey$channel)
d.clean.survey$channel <-  gsub("qualtrics", "Qualtrics", d.clean.survey$channel)

# Make Survey Monkey timestamp length consistent Compliance Check
d.clean.survey[nchar(d.clean.survey$start_date) == 12,]$start_date <- gsub(" ", " 0", d.clean.survey[nchar(d.clean.survey$start_date) == 12,]$start_date)
d.clean.survey[nchar(d.clean.survey$end_date) == 12,]$end_date <- gsub(" ", " 0", d.clean.survey[nchar(d.clean.survey$end_date) == 12,]$end_date)

# Preview data
head(d.clean.survey)

# Save in CSV as backup
write.csv(d.clean.survey, file = "d_clean_survey.csv")

```

Ok, so. I think that you've got some issues in the model that you've written. And, unfortunately, the way you've got your data stored, I cannot recreate the *full* set of data that you'd need to esitmate the **correct** model, but I can get you pretty close. 

1. For each choice that a person made, there were **four** options that they could have chosen, right? The four cards. 
2. What you've got recorded is the binary indicaton if they chose a *male* or *female* person in for that choice. 
3. So, while the ideal data, I think, would have four rows for each choice that a person made, instead, I'm going to collapse the two options that are *male* and the two options that are *female*. 
4. This is going to leave you with a set of choices for each of `pcp`, `cardiologist`, `psychiatrist`, `dentist`. 

```{r alex_models}
d <- fread('./d_clean_survey.csv')
d <- d[ , .(respondent_id, gender, pcp, cardiologist, psychiatrist, dentist)]
d <- d[complete.cases(d), ]

d[ , ':='(
  pcp_female = pcp == 'Female', 
  pcp_male = !(pcp == 'Female'), 
  cardiologist_female = cardiologist == 'Female', 
  cardiologist_male = !(cardiologist == 'Female'), 
  psychiatrist_female = psychiatrist == 'Female', 
  psychiatrist_male = !(psychiatrist == 'Female'), 
  dentist_female = dentist == 'Female', 
  dentist_male = !(dentist == 'Female'))
  ]
d[ , ':='(
  pcp = NULL, 
  cardiologist = NULL, 
  psychiatrist = NULL, 
  dentist = NULL)
  ]

setkeyv(d, 'respondent_id')

tall_data <- expand.grid(
  respondent_id = d[ , respondent_id], 
  specialty = c('pcp', 'cardiologist', 'psychiatrist', 'dentist'), 
  doctor_gender = c('male', 'female')
  )

tall_data <- data.table(tall_data)
setkeyv(tall_data, cols = c('respondent_id', 'specialty', 'doctor_gender'))

pcp_female <- merge(
  tall_data[specialty == 'pcp' & doctor_gender == 'female'], 
  d[ , .(respondent_id, 'choice' = pcp_female, 'subject_gender' = gender)], 
  by = 'respondent_id'
  )
pcp_male <- merge(
  tall_data[specialty == 'pcp' & doctor_gender == 'male'], 
  d[ , .(respondent_id, 'choice' = pcp_male, 'subject_gender' = gender)], 
  by = 'respondent_id'
)
cardiologist_female <- merge(
  tall_data[specialty == 'cardiologist' & doctor_gender == 'female'], 
  d[ , .(respondent_id, 'choice' = cardiologist_female, 'subject_gender' = gender)], 
  by = 'respondent_id'
)
cardiologist_male <- merge(
  tall_data[specialty == 'cardiologist' & doctor_gender == 'male'], 
  d[ , .(respondent_id, 'choice' = cardiologist_male, 'subject_gender' = gender)], 
  by = 'respondent_id'
)
psychiatrist_female <- merge(
  tall_data[specialty == 'psychiatrist' & doctor_gender == 'female'], 
  d[ , .(respondent_id, 'choice' = psychiatrist_female, 'subject_gender' = gender)],
  by = 'respondent_id'
)
psychiatrist_male <- merge(
  tall_data[specialty == 'psychiatrist' & doctor_gender == 'male'], 
  d[ , .(respondent_id, 'choice' = psychiatrist_male, 'subject_gender' = gender)],
  by = 'respondent_id'
)
dentist_female <- merge(
  tall_data[specialty == 'dentist' & doctor_gender == 'female'], 
  d[ , .(respondent_id, 'choice' = dentist_female, 'subject_gender' = gender)],
  by = 'respondent_id'
)
dentist_male <- merge(
  tall_data[specialty == 'dentist' & doctor_gender == 'male'], 
  d[ , .(respondent_id, 'choice' = dentist_male, 'subject_gender' = gender)],
  by = 'respondent_id'
)

tall_data_2 <- rbind(
  pcp_female, pcp_male,
  cardiologist_female, cardiologist_male,
  psychiatrist_female, psychiatrist_male,
  dentist_female, dentist_male
  )

tall_data_2 <- data.table(tall_data_2)
tall_data_2 <- tall_data_2[complete.cases(tall_data_2)]

mod_1 <- tall_data_2[ , lm(choice ~ doctor_gender)]
mod_1$cluster_se <- sqrt(diag(vcovCL(mod_1, tall_data_2[ , respondent_id])))

mod_2 <- tall_data_2[ , lm(choice ~ specialty * doctor_gender)]
mod_2$cluster_se <- sqrt(diag(vcovCL(mod_2, tall_data_2[ , respondent_id])))

doctor_specialty_predictions <- data.table(
  expand.grid(
    'specialty' = c('pcp', 'cardiologist', 'psychiatrist', 'dentist'), 
    'doctor_gender' = c('female', 'male')
  )
)

doctor_specialty_predictions <- cbind(
  doctor_specialty_predictions, 
  predict(mod_2, newdata = doctor_specialty_predictions, interval = 'confidence')
)

mod_3 <- tall_data_2[ , lm(choice ~ doctor_gender * subject_gender)]
summary(mod_3)

mod_4 <- tall_data_2[ , lm(choice ~ specialty * doctor_gender * subject_gender)]
summary(mod_4)
```

 I'll leave the team to interpret each of these models. 



```{r}
##################################### Part 1.5: Compliance Check - add duration column and plot
#### result dataframe:  d.clean.survey

# Calculate durartion(in minutes) to complete survey 
d.clean.survey$duration_min[d.clean.survey$channel=="SurveyMonkey"] <-  ( as.numeric(substr(d.clean.survey$end_date[d.clean.survey$channel=="SurveyMonkey"], 3, 4)) - as.numeric(substr(d.clean.survey$start_date[d.clean.survey$channel=="SurveyMonkey"], 3, 4)) ) * 1440 + (as.numeric(substr(d.clean.survey$end_date[d.clean.survey$channel=="SurveyMonkey"], 9, 10)) - as.numeric(substr(d.clean.survey$start_date[d.clean.survey$channel=="SurveyMonkey"], 9, 10)) ) * 60  +  (  as.numeric(substr(d.clean.survey$end_date[d.clean.survey$channel=="SurveyMonkey"], 12, 13))  - as.numeric(substr(d.clean.survey$start_date[d.clean.survey$channel=="SurveyMonkey"], 12, 13)) )

d.clean.survey$duration_min[d.clean.survey$channel=="Qualtrics"] <-  ( as.numeric(substr(d.clean.survey$end_date[d.clean.survey$channel=="Qualtrics"], 9, 10)) - as.numeric(substr(d.clean.survey$start_date[d.clean.survey$channel=="Qualtrics"], 9, 10)) ) * 1440 + ( as.numeric(substr(d.clean.survey$end_date[d.clean.survey$channel=="Qualtrics"], 12, 13)) - as.numeric(substr(d.clean.survey$start_date[d.clean.survey$channel=="Qualtrics"], 12, 13)) ) * 60  +  (  as.numeric(substr(d.clean.survey$end_date[d.clean.survey$channel=="Qualtrics"], 15, 16))  -  as.numeric(substr(d.clean.survey$start_date[d.clean.survey$channel=="Qualtrics"], 15, 16))) + ( as.numeric(substr(d.clean.survey$end_date[d.clean.survey$channel=="Qualtrics"], 18, 19))  -  as.numeric(substr(d.clean.survey$start_date[d.clean.survey$channel=="Qualtrics"], 18, 19)))/60

# Preview data
head(d.clean.survey)

d.clean.survey$duration_min_category <- case_when(
  d.clean.survey$duration_min <=1 ~ "layer0: Less than 1 minute",
  d.clean.survey$duration_min <=2 & d.clean.survey$duration_min > 1  ~ "layer1:  1~2 minutes",
  d.clean.survey$duration_min <=3 & d.clean.survey$duration_min > 2  ~ "layer2:  2~3 minutes",
  d.clean.survey$duration_min <=4 & d.clean.survey$duration_min > 3  ~ "layer3:  3~4 minutes",
  d.clean.survey$duration_min <=5 & d.clean.survey$duration_min > 4  ~ "layer4:  4~5 minutes",
  d.clean.survey$duration_min <=10 & d.clean.survey$duration_min > 5  ~ "layer5:  5~10 minutes",
  d.clean.survey$duration_min <=20 & d.clean.survey$duration_min > 10  ~ "layer6: 10~20 minutes",
  d.clean.survey$duration_min <=100 & d.clean.survey$duration_min > 20  ~ "layer7: 20~100 minutes",
  d.clean.survey$duration_min <=1000 & d.clean.survey$duration_min > 100  ~ "layer8: 100~1000 minutes",
  d.clean.survey$duration_min > 1000  ~ "layer9: More than 1000 minutes")

ggplot(data=d.clean.survey, aes(x=duration_min_category, fill=duration_min_category)) +
  geom_bar() +
  geom_text( stat='count' , aes(label=..count..), vjust=-0.5) +
  scale_x_discrete(labels = wrap_format(10)) + 
  theme(legend.position = "none") +
  xlab("Time to Complete Survey (in minutes)")

# # Compliance Check: duration_min distribution from 0 to 5.9k
# ggplot(data.frame(d.clean.survey[d.clean.survey$duration_min<=20,]), aes(y=duration_min)) +
#   geom_boxplot(outlier.colour="red", outlier.shape=1,outlier.size=4)
# 
# ggplot(data.frame(d.clean.survey[d.clean.survey$duration_min>20 & d.clean.survey$duration_min<1000,]), aes(x=duration_min)) +
#   geom_bar() + 
#     coord_cartesian(xlim = c(20, 1000))
# 
# ggplot(data.frame(d.clean.survey[d.clean.survey$duration_min>1000,]), aes(x=duration_min)) +
#   geom_bar() + 
#     coord_cartesian(xlim = c(1000, 6000))
# 
# # Compliance Check: duration_min < 2 minutes, considered as not a valid feedback
# nrow(d.clean.survey[d.clean.survey$duration_min<1,]) # 4 rows
# nrow(d.clean.survey[d.clean.survey$duration_min<2,]) # 56 rows


```

```{r}
d <- d.clean.model
d[,.N]
d[gender=="Male",.N]/d[gender=="Female",.N]

ggplot(data=d.clean.survey, aes(x=income, fill=income)) +
  geom_bar() +
  geom_text( stat='count' , aes(label=..count..), vjust=-0.5) +
  scale_x_discrete(labels = wrap_format(10)) + 
  theme(legend.position = "none") +
  xlab("Time to Complete Survey (in minutes)")


```



```{r}
##################################### Part 2: Generate Modeling Data: add Y and other Outcome Variable for modeling use
#### result dataframe:  d.clean.model
#### result dataframe:  d.clean.model.trans

# Genderate Y for 4 non-gender-specific specialty
d.clean.model <- d.clean.survey

d.clean.model[,Y_pcp := ifelse(gender==pcp, 1, -1)]
d.clean.model[,Y_cardio := ifelse(gender==cardiologist, 1, -1)]
d.clean.model[,Y_psy := ifelse(gender==psychiatrist, 1, -1)]
d.clean.model[,Y_den := ifelse(gender==dentist, 1, -1)]
d.clean.model[,Y_1 := Y_pcp + Y_cardio + Y_psy + Y_den]

# Generate #of Famele/Male within 3 specs
d.clean.model$Y_4spec_female <- str_count(paste(d.clean.model$pcp, d.clean.model$cardiologist, d.clean.model$psychiatrist, d.clean.model$dentist), "Female")
d.clean.model$Y_4spec_male <- str_count(paste(d.clean.model$pcp, d.clean.model$cardiologist, d.clean.model$psychiatrist, d.clean.model$dentist), "Male")
d.clean.model <- d.clean.model[(d.clean.model$Y_4spec_female + d.clean.model$Y_4spec_male) == 4,]


######## Create transpose dataframe
d.clean.model.trans  <- melt(d.clean.model[,c(2, 7, 11:14)], id.vars=c("respondent_id","gender"),  
                             variable.name = "specialty", value.name="gender_selected", na.rm=TRUE)

d.clean.model.trans[, Y_if_female := ifelse(gender_selected=="Female", 1, 0)]
d.clean.model.trans[, isfemale := ifelse(gender=="Female", 1, 0)]

# Preview data
head(d.clean.model)
head(d.clean.model.trans)

```

```{r}

##################################### Part 3: EDA for Covarites 
library(scales)

d.cov.eda <- d.clean.survey

d.cov.eda$year_of_birth_range <- case_when(
  d.cov.eda$year_of_birth >= 1930 & d.cov.eda$year_of_birth < 1940 ~ "1930~1939",
  d.cov.eda$year_of_birth >= 1940 & d.cov.eda$year_of_birth < 1950 ~ "1940~1949",
  d.cov.eda$year_of_birth >= 1950 & d.cov.eda$year_of_birth < 1960 ~ "1950~1959",
  d.cov.eda$year_of_birth >= 1960 & d.cov.eda$year_of_birth < 1970 ~ "1960~1969",
  d.cov.eda$year_of_birth >= 1970 & d.cov.eda$year_of_birth < 1980 ~ "1970~1979",
  d.cov.eda$year_of_birth >= 1980 & d.cov.eda$year_of_birth < 1990 ~ "1980~1989",
  d.cov.eda$year_of_birth >= 1990 & d.cov.eda$year_of_birth < 2000 ~ "1990~1999",
  d.cov.eda$year_of_birth >= 2000 & d.cov.eda$year_of_birth < 2010 ~ "2000~2009",
  d.cov.eda$year_of_birth >= 2010 & d.cov.eda$year_of_birth < 2020 ~ "2010~2019",
  TRUE ~ "other"
)

d.cov.eda$age_range <- case_when(
  d.cov.eda$year_of_birth < 1960 ~ "60+",
  d.cov.eda$year_of_birth >= 1960 & d.cov.eda$year_of_birth < 1975 ~ "45~60",
  d.cov.eda$year_of_birth >= 1975 & d.cov.eda$year_of_birth < 1990 ~ "30~44",
  d.cov.eda$year_of_birth >= 1990 & d.cov.eda$year_of_birth < 2002 ~ "18~29",
  d.cov.eda$year_of_birth >= 2002 & d.cov.eda$year_of_birth < 2020 ~ "18-",
  TRUE ~ "other"
)

d.cov.eda %>% 
    count(age_range = factor(age_range), gender = factor(gender)) %>% 
    mutate(pct = prop.table(n)) %>% 
    ggplot(aes(x = age_range, y = pct, fill = gender, label = scales::percent(pct))) + 
    geom_col(position = 'stack') +     
    theme(legend.position = c(0.9, 0.85), axis.text.x = element_text(angle = 0, hjust = 1)) +
    geom_text(position = position_stack(vjust = 0.5),
              size = 3) + 
    scale_y_continuous(labels = scales::percent)   #  #labels=function(x) paste0(x,"%")


d.cov.eda %>% 
    count(race = factor(race), gender = factor(gender)) %>% 
    mutate(pct = prop.table(n)) %>% 
    ggplot(aes(x = race, y = pct, fill = gender, label = scales::percent(pct))) + 
    geom_col(position = 'stack') +     
    theme(legend.position = c(0.7, 0.85), axis.text.x = element_text(angle = 0, hjust = 1)) +
    scale_x_discrete(labels = wrap_format(10)) + 
    geom_text(position = position_stack(vjust = 0.5),
              size = 3) + 
    scale_y_continuous(labels = scales::percent)   #  #labels=function(x) paste0(x,"%")


# unique(d.cov.eda$degree)
d.cov.eda$degree_order <- case_when(
  d.cov.eda$degree == "Less than high school Degree" ~ "0-Less than high school Degreee",
  d.cov.eda$degree == "High School Graduate" ~ "1-High School Graduate",
  d.cov.eda$degree == "Associate Degree (2-year)" ~ "2-Associate Degree (2-year)",
  d.cov.eda$degree == "Bachelor's Degree (4-year)" ~ "3-Bachelor's Degree (4-year)",
  d.cov.eda$degree == "Master's Degree" ~ "4-Master's Degree",
  d.cov.eda$degree == "Doctoral Degree" ~ "5-Doctoral Degree",
  d.cov.eda$degree == "Professional Degree (MD, JD etc.)" ~ "6-Professional Degree (MD, JD etc.)")


d.cov.eda %>% 
    count(degree = factor(degree_order), gender = factor(gender)) %>% 
    mutate(pct = prop.table(n)) %>% 
    ggplot(aes(x = degree, y = pct, fill = gender, label = scales::percent(pct))) + 
    geom_col(position = 'stack') +     
    theme(legend.position = c(0.9, 0.85), axis.text.x = element_text(angle = 0, hjust = 1)) +
    scale_x_discrete(labels = wrap_format(10)) + 
    geom_text(position = position_stack(vjust = 0.5),
              size = 3) + 
    scale_y_continuous(labels = scales::percent)   #  #labels=function(x) paste0(x,"%")


# unique(d.cov.eda$income)
d.cov.eda$income_edge <- case_when(
  d.cov.eda$income == "$50,000 to $99,999" ~ 50000,
  d.cov.eda$income == "$200,000 or more" ~ 200000,
  d.cov.eda$income == "$10,000 to $49,999" ~ 10000,
  d.cov.eda$income == "$100,000 to $149,999" ~ 100000,
  d.cov.eda$income == "Less than $10,000" ~ 0,
  d.cov.eda$income == "$150,000 to $199,999" ~ 150000)

d.cov.eda %>% 
    count(income = factor(income_edge), gender = factor(gender)) %>% 
    mutate(pct = prop.table(n)) %>% 
    ggplot(aes(x = income, y = pct, fill = gender, label = scales::percent(pct))) + 
    geom_col(position = 'stack') +     
    theme(legend.position = c(0.9, 0.85), axis.text.x = element_text(angle = 0, hjust = 1)) +
    scale_x_discrete(labels = wrap_format(10)) + 
    geom_text(position = position_stack(vjust = 0.5),
              size = 3) + 
    scale_y_continuous(labels = scales::percent)   #  #labels=function(x) paste0(x,"%")




```
```{r}
# Covariate balance check
library(cobalt)
d <- d.clean.model
#data(d, package="cobalt")
#d[, bal.tab(Y_4spec_female ~ income, datweights = "att.weights",
#     distance = "p.score", method = "weighting")]
d[, gender_n := ifelse(gender=="Female", 1, 0)]
model1 <- d[, lm(gender_n ~ gender_n)]

```

```{r}
##################################### Part 4: EDA for Outcome Variables 
ggplot(data.frame(d.clean.model), aes(x=Y_1, fill=gender)) +
  geom_bar() 

```
```{r}
# Overall averages
d <- d.clean.model[,c("gender","Y_4spec_female")]
d <- na.omit(d)

total <- d[,.N]
all <- d[, .(pct_all = (.N/total*100)), keyby=(Y_4spec_female)]
ggplot(data=all, aes(x=factor(Y_4spec_female), y=pct_all)) + geom_bar(stat="identity") + labs(x = "Number of female doctors chosen per subject in the survey") + labs(y = "% of subjects") + labs(title = "Distribution of Female physician count")

# Gender specific averages
d[gender=="Male", .N]/d[,.N]
d[gender=="Female", .N]/d[,.N]

d <- na.omit(d.clean.model[,c("gender", "Y_4spec_female")])
all<-d[, .(pct_all = (.N/total*100)), keyby=.(gender, Y_4spec_female)]
ggplot(data=all, aes(x=factor(Y_4spec_female), y=pct_all, fill=gender)) + geom_bar(stat="identity", 
                                                                  position=position_dodge()) + labs(x = "Number of female doctors chosen per subject in the survey") + labs(y = "% of subjects") + labs(title = "Distribution of Female physician count") + guides(fill = guide_legend(title = "Subject gender"))


```
```{r}
d[, .(pct_all = (.N/total*100)), keyby=list(gender, Y_4spec_female)]
```



```{r}
# Overall averages
d <- d.clean.model[,c("gender","Y_1")]
d <- na.omit(d)

total <- d[,.N]
all <- d[, .(pct_all = (.N/total*100)), keyby=(Y_1)]
ggplot(data=all, aes(x=factor(Y_1), y=pct_all)) + geom_bar(stat="identity")

# Gender specific averages
d[gender=="Male", .N]/d[,.N]
d[gender=="Female", .N]/d[,.N]

d <- na.omit(d.clean.model[,c("gender", "Y_1")])
all<-d[, .N, keyby=.(gender, Y_1)]
ggplot(data=all, aes(x=factor(Y_1), y=N, fill=gender)) + geom_bar(stat="identity", 
                                                                  position=position_dodge())
```
```{r}
d <- d.clean.model
d[, mean(Y_4spec_female)]
```
```{r}
d <- d.clean.model
all <- d[, .(pct_all = (.N/total*100)), keyby=.(gender)]
ggplot(data=all, aes(x=factor(gender), y=pct_all, fill=gender)) + geom_bar(stat="identity", position=position_dodge())
```



```{r}
# Effects by gender and speciality

plot_by_specialty <- function(spec) {
  d <- na.omit(d.clean.model.trans[specialty==spec, c("gender","Y_if_female","isfemale")])
  all <- d[, .(pct_all = (.N/total*100)), keyby=.(gender, Y_if_female)]
  
  ggplot(data=all, aes(x=factor(Y_if_female), y=pct_all, fill=gender)) + geom_bar(stat="identity", position=position_dodge()) + labs(x = paste("Number of female ",spec,"s chosen per subject in the survey", sep='')) + labs(y = "% of subjects") + labs(title = "Distribution of Female physicians") + guides(fill = guide_legend(title = "Subject gender"))
}

plot_by_specialty("pcp")
plot_by_specialty("cardiologist")
plot_by_specialty("psychiatrist")
plot_by_specialty("dentist")
```




```{r}
# Income effects
d <- na.omit(d.clean.survey[,c("income","Y_1")])
total <- d[,.N]
all<-d[, .(pct = (.N/total)), keyby=.(income, Y_1)]
ggplot(data=all, aes(x=factor(Y_1), y=pct, fill=income)) + geom_bar(stat="identity",
                                                                    position=position_dodge())

```
```{r}
# Race effects
d <- na.omit(d.clean.survey[,c("race","Y_1")])
total <- d[,.N]
all<-d[, .(pct = (.N/total)), keyby=.(race, Y_1)]
ggplot(data=all, aes(x=factor(Y_1), y=pct, fill=race)) + geom_bar(stat="identity",
                                                                    position=position_dodge())
```
```{r}
# covariate balance check
d <- na.omit(d.clean.model.trans)

total <- d[,.N]
d[Y_if_female==0, .N]/total
d[Y_if_female==1, .N]/total

d[,.(mean(Y_4spec_female))]


#t.test(d[Y_if_female==0,], d[Y_if_female==1,])

bal_check_gender <- d[, lm(Y_if_female ~ isfemale)]
bal_check_specialty <- d[, lm(Y_if_female ~ specialty)]

library(cobalt)
d <- d.clean.model.trans
covs <- subset(d, select = c(gender))
d$p.score <- glm(f.build("isfemale", covs), data = d, 
                       family = "binomial")$fitted.values
d$att.weights <- with(d, isfemale + (1-isfemale)*p.score/(1-p.score))


b <- bal.tab(covs, treat = d$isfemale, data = d.clean.model.trans, weights = d$att.weights, method = 'weighting')
b

```
```{r}
d <- d.clean.model
model1 <- d[,lm(Y_1 ~ gender)]
stargazer(model1, type="text")
summary(model1)
d[gender=="Male", .(mean(Y_1))]
```



```{r}
d <- d.clean.model
d <- d[, age := (2019 - as.numeric(year_of_birth))]
m_age <- d[, lm(Y_4spec_female ~ gender + age + gender * age)]
stargazer(m_age, type="text", p.auto = TRUE)
summary(m_age)
```
```{r}
d[gender=="Male" & age==30, .(mean(Y_4spec_female))]
```





```{r}
d <- d.clean.model
d <- na.omit(d)
m_gender <- d[, lm(Y_4spec_female ~ gender)]
stargazer(m_gender, type="text", p.auto = TRUE)

d[, gender_n := ifelse(gender=="Male", 0, 1)]
d[,cor(gender_n, Y_4spec_female)]
```

```{r}
d[gender=="Male", .(mean(Y_4spec_female))]
d[gender=="Female", .(mean(Y_4spec_female))]
```
```{r}
library(car)
d <- d.clean.model[,c("gender", "Y_4spec_female")]
d[, scatterplot(Y_4spec_female ~ as.factor(gender))]
```
```{r}
d <- d.clean.model.trans
model1 <- d[, lm(Y_if_female ~ Y_if_female + isfemale + Y_if_female * isfemale)]
stargazer(model1, type = "text")
```
```{r}
cse <- function(model, cl) {
  vcov <- vcovCL(model, cluster=cl)
  sqrt(diag(vcov))
}

d <- na.omit(d.clean.model.trans)
model2 <- d[, lm(Y_if_female ~ Y_if_female + isfemale + Y_if_female * isfemale)]
model2$vcovCL_ <- vcovCL(model2, cluster = d[, respondent_id])
coeftest(model2, model2$vcovCL)
model2$cse <- cse(model2, d[, respondent_id])
stargazer(model2, type="text")
```


```{r}
total <- d[,.N]
d[isfemale==1 & Y_if_female==1, .N/total]
d[isfemale==1 & Y_if_female==0, .N/total]
d[isfemale==0 & Y_if_female==0, .N/total]
d[isfemale==0 & Y_if_female==1, .N/total]
```




```{r}
d <- d.clean.survey[,c("channel", "gender","race","income","degree","Y_1")]
d <- na.omit(d)
```

```{r}
# Model 1 - Effect of participant gender on outcome
m_gender <- d[, lm(Y_1 ~ gender)]
summary(m_gender)
```




```{r}
# Model 2 - Effet of participant race on outcome
m_income <- d[, lm(Y_4spec_female ~ gender + income + gender * income)]
summary(m_income, type="text")

d[income == "Less than $10,000" & gender=="Male", .(mean(Y_4spec_female))]
```

```{r}
# Model 3 - Effect of participant degree on outcome
d <- na.omit(d)
m_degree <- d[, lm(Y_4spec_female ~ gender + degree + gender*degree)]
summary(m_degree)
```

```{r}
# Model 4 - Effect of participant income on outcome
m_income <- d[, lm(Y_1 ~ income)]
summary(m_income)
```

```{r}
# Model 5 - Interaction effect of gender and race
m_gender_race <- d[, lm(Y_4spec_female ~ gender + race + gender * race)]
summary(m_gender_race)
```
```{r}
# Model 6 - Interaction effect of gender and race
m_gender_income <- d[, lm(Y_1 ~ gender + income + gender * income)]
stargazer(m_gender_income, type = "text")
```
```{r}
# Model 7 - Interaction effect of gender and degree
m_gender_degree <- d[, lm(Y_4spec_female ~ gender + degree + gender * degree)]
summary(m_gender_degree)
```
```{r}
# Model 7 - Interaction effect of gender and degree
d <- d.clean.model
d[, age := (2019-yea]
m_gender_degree <- d[, lm(Y_4spec_female ~ gender + degree + gender * degree)]
summary(m_gender_degree)
```



```{r}
d <- d.clean.model
d_gender_spec_male <- d[channel=="Qualtrics"]
d_gender_spec_male[, Y_specific := (gender_specific_score3 + gender_specific_score4)-(gender_specific_score1 + gender_specific_score2)]
d_gender_spec_male[gender=="Male",mean(Y_specific)]
model1 <- d_gender_spec_male[, lm(Y_specific ~ gender)]
stargazer(model1, type="text")
summary(model1)
```

```{r}
# Use stargazer to consolidate all the models
stargazer(m_gender, 
          m_degree, 
          m_race,
          m_gender_race,
          m_gender_income,
          m_gender_degree,
          type="text")


```